Make any stupid plot you want

### 2020-12-22 draft/sections/math.tex
what is P"

\subsection{Fiber Bundles}
We provide a brief introduction to fiber bundles because we model data, visual transformations, and a prerendered visual graphic as fiber bundles. A fiber bundle is a structure $(E, B, \pi, F)$  consisting of topological total space $E$, base space $K$, fiber space $F$ and the map from total space to base space:

@@

The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$
\begin{equation}
    \label{eq:section_domain}
    \pi(f(b)) = b \text{ for all } b \in B 
\end{equation}

@@

\subsection{Data Model}
As proposed by Butler \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, we model data as a fiber bundle:
\begin{equation}
    \label{eq:data_fiber_bundle}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi"] & B
    \end{tikzcd}
\end{equation}

with a total space $E$, fiber space $F$, and base space $K$ which can be thought of as a set of keys $k$. The section $\tau:K \rightarrow E$ is an instance of the data that lies in $E$ and is discussed in section~\ref{sec:data_fiber}.

@@

\subsection{Prerender Space}
\label{sec:display}

Every point $k \in K$ maps to a space $S_{k} \in S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber dependent on the render space and a base space of $S$:
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[r, "\pi"] &S\\   
        \end{tikzcd}
\end{equation}

\subsubsection{Section $\rho$}

A section $\rho: S \rightarrow H$
\begin{equation}
    \begin{tikzcd}
        D \arrow[r, hook] & H \arrow[d, "\pi"']              \\
                          & S \arrow[u, "\rho"', bend right]
        \end{tikzcd}
\end{equation}

 is a mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to visual space as defined in D. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

@@

In this section we will define the artist as a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}
The artist decomposes to data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$. In order to define $A$, we first define the visual fiber bundle $V$ that shares basespace $K$ with $E$:

\begin{equation}
    \begin{tikzcd}
        P \arrow[r, hook] & V \arrow[r, "\pi"] & K\\   
    \end{tikzcd}
\end{equation}

with fiber $P$ that encodes visual parameters such as position or color. The section $\mu: V \rightarrow K$

\begin{equation}
    \begin{tikzcd}
        P \arrow[r, hook] & V \arrow[d, "\pi"']              \\
                          & K \arrow[u, "\mu"', bend right]
        \end{tikzcd}
\end{equation}

returns a record in $P$. The fiber $P$ is the space of visual parameters %% defined like P, dependent on Q, P is targeting our library

\subsubsection{Data Screen Mapping}
The data bases pace $K$ can be considered a subspace of the screen base space $S$ such that $\xi: S \rightarrow K$ is a deformation retraction
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

>>>>

\subsection{Fiber Bundles}
We provide a brief description of fiber bundles because we model data, visual transformations, and a prerendered visual graphic as fiber bundles. A fiber bundle is a structure $(E, B, \pi, F)$  consisting of topological total space $E$, base space $K$, fiber space $F$ and the map from total space to base space:

@@

\subsubsection{Section}
The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & B \arrow[u, "f"', bend right]
    \end{tikzcd}
\end{equation}

such that $f$ is the right inverse of $\pi$
\begin{equation}
    \label{eq:section_domain}
    \pi(f(b)) = b \text{ for all } b \in B 
\end{equation}

@@

\subsection{Data Model}
As proposed by Butler \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, we model data as a fiber bundle (E, K, $\pi$, F) with $\pi: E \rightarrow K$ where $K$ which can be thought of as a set of keys $k$. A section $\tau:K \rightarrow E$ is an instance of the data that lies in $E$ and is discussed in section~\ref{sec:data_fiber}.

@@

\subsection{Prerender Space}
\label{sec:display}
We model the prerender space on which lives on ideal version of the visulaization as a fiber bundle (H, S, $\pi$, D). $H$ is the predisplay space, with a fiber $D$ dependent on the target physical display and a base space of $S$.

\subsubsection{Base space}
$K$ can be considered a subspace of the screen base space $S$ such that $\xi: S \rightarrow K$ is a deformation retraction \cite{RetractionTopology2020}
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

\subsubsection{Fiber and Section}
A section $\rho: S \rightarrow H$ is a mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to visual space as defined in D. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, r, g, b, a\}
    \label{eq:rho}
\end{equation}

@@

In this section we will define the artist as a mapping from the sheaf $O(E)$ representing the data to a pre-render space $O(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}
The artist decomposes to data $E$ to visual mappings $V$ and $V$ mappings composited to a visual in prerender space $H$. In order to define $A$, we first define the visual fiber bundle $V$ that shares basespace $K$ with $E$ as ($V$,$K$, $\pi$, $P$) with section $\mu: V \rightarrow K$. The fiber $P$ is the space of visual variables $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} that can be encoded in the visualization being generated by $A$.

\subsubsection{Example}
If for example, a line artist as defined in \cite{Matplotlib} only supported the visual mappings xposition, yposition, width, color, style; then the $P$ for this line artist would be:
\begin{itemize}
    \item $C = \{\text{xposition, yposition, linewidth, color, linestyle}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f\}$ 
    \item $\sigma: C \rightarrow DT$ 
    \item $P = \Gamma(\sigma) = \Gamma(\mu)$ 
\end{itemize}
